How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-05 tse-paper/content.tex
Include minor fixes

Finally, from the fields of information retrieval (IR) and natural
language
processing (NLP, see \Cref{tab:litsur:techniques}), we leverage widely-used text similarity measures and call this approach \emph{Common Text Similarity (CTS)}.
The intuition behind it is that the relevant,
failing parts of build logs often look similar to each other, even if
the exact failure reasons might differ.

@@

\subsubsection{Configuring}
To configure CTS we chose to use the same concept of examples as for
PBE: lines of the targeted chunks from the training examples define
the search query.
Using a Vector Space
Model~\cite{schutze2008introduction} (VSM), an algebraic model for
representing textual documents, we encode each line as a separate term
vector.
The terms that make up the dictionary are simply all words
that appear in the example logs, where we separate words by spaces and
punctuation.
The vectors comprise points counting
how many times a word out of the dictionary appears in the specific
line at hand.

@@

\section{Future Work}
In this section, we describe what we believe are fruitful future
research directions in the field of build log analysis.
We base our
assessment on the results of the literature survey and combine it with
findings from our technique comparison study.

@@

\textbf{Refinement of Retrieval Quality.} We
investigated basic configurations of existing techniques applied to
chunk retrieval from build logs.
In a next step, each of these
techniques could be refined to better customize it to the domain of build
logs.
The \emph{LogChunks} data set and our study results act as a
baseline to benchmark such technique improvements.
We propose the
following improvements:
\begin{itemize}[leftmargin=0.4cm]
  \item \textbf{Custom Ranking and Tokens for PBE.} Program
  synthesis through PROSE ranks possible programs according to
  what the user most likely intended.
  One could adapt the ranking
  rules provided by the FlashExtract DSL to fit common build log
  chunk retrieval tasks.
  FlashExtract includes special tokens when
  enumerating possible regular expressions.
  One could extend these
  with tokens found in build logs, such as ``-,''
	``=,'' ``ERROR,''
  or ``[OK]'' to improve results.
  \item \textbf{Meta-Parameter Optimization for CTS.} Information
  retrieval techniques have various meta-parameters which can be
  optimized for the specific use
  case~\cite{panichella2016parameterizing}.
  We propose to further
  investigate improvements in preprocessing of the log text, in
  tokenization of the log lines into terms, and in stop words
  lists.
\end{itemize}

>>>>

Finally, from the fields of information retrieval (IR) and natural
language
processing (NLP, see \Cref{tab:litsur:techniques}), we leverage
a widely-used text similarity measure and call this approach \emph{Common
Text Similarity (CTS)}.
The intuition behind it is that the relevant,
failing parts of build logs often look similar to each other, even if
the exact failure reasons might differ.

@@

\subsubsection{Configuring}
To configure CTS we chose to use the same concept of examples as for
PBE: lines of the targeted chunks from the training examples define
the search query.
Using a Vector Space
Model~\cite{schutze2008introduction} (VSM), an algebraic model for
representing textual documents, we encode each line as a separate term
vector.
The terms that make up the dictionary are simply all words
that appear in the example logs. We separate words by spaces and
punctuation.
The vectors comprise points counting
how many times a word out of the dictionary appears in the specific
line at hand.

@@

\section{Future Work}
In this section, we give an outline of fruitful future
research directions in the field of build log analysis.
We base our
suggestions on the results of the literature survey and the
findings from our technique comparison study.

@@

One could also interpret the techniques we implemented
differently. For example, for CTS, we look for similarity between the
lines we want to extract. One could find similarity between the
context that surrounds them, instead of the actual chunk to be
extracted. The intuition behind this approach would be that often the
error chunk is variable, but the context around it is
stable---essentially the principle by which extraction by PBE
works. Such a version of ``inverse CTS'' might yield better retrieval
results.

\textbf{Refinement of Retrieval Quality.} We
investigated basic configurations of existing techniques applied to
chunk retrieval from build logs.
In a next step, each of these
techniques could be refined to better customize it to the domain of build
logs.
The \emph{LogChunks} data set and our study results can act as a
baseline to benchmark such technique improvements.
We propose the
following improvements:
\begin{itemize}[leftmargin=0.4cm]
  \item \textbf{Custom Ranking and Tokens for PBE.} Program
  synthesis through PROSE ranks possible programs according to
  what the user most likely intended.
  One could adapt the ranking
  rules provided by the \emph{FlashExtract} DSL to fit common build log
  chunk retrieval tasks.
  \emph{FlashExtract} includes special tokens when
  enumerating possible regular expressions~\cite{le2014flashextract:}.
  One could extend these
  with tokens found in build logs, such as ``-,''
	``=,'' ``ERROR,''
  or ``[OK]'' to improve results.
  \item \textbf{Meta-Parameter Optimization for CTS.} Information
  retrieval techniques have various meta-parameters which can be
  optimized for the specific use
  case~\cite{panichella2016parameterizing}.
  We propose to further
  investigate improvements in preprocessing of the log text, in
  tokenization of the log lines into terms, and in stop words
  lists.

  For CTS, we currently have no concept of semantic
  similarity. Therefore, the synonyms ``Fail'' and ``Failure'' would
  fall into two different frequency counts. Using a
  wordnet~\cite{pedersen2004wordnet} or other NLP techniques to
  capture synonyms might improve similarity measure between related
  lines, and therefore overall performance of CTS.
\end{itemize}
